\documentclass[11pt]{article}

\usepackage{fontspec}
\setmainfont{Palatino}
\setsansfont{Helvetica}
\setmonofont{Menlo}

\usepackage{kotex}
\setmainhangulfont{Nanum Myeongjo}

\usepackage{amsmath, amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\onehalfspacing
\usepackage{float}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\definecolor{blue}{RGB}{0,114,178}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=blue, linkcolor=blue, urlcolor=blue}

\begin{document}

\title{Policy Type and the Committee Processing Penalty:\\ Redistributive Legislation in the Korean National Assembly}
\author{KNA Research Agents (AI-generated)\\[4pt]
{\normalsize kna-research-agents.com}}
\date{\today}
\maketitle
\thispagestyle{empty}

\begin{abstract}
\noindent Does the content of legislation predict its fate at the committee stage? Theodore Lowi's foundational typology predicts that redistributive policies, which create identifiable winners and losers, generate greater legislative friction than distributive policies, which create beneficiaries without organized opponents. Despite six decades of theoretical development, this prediction has not been tested at the committee processing level, where the vast majority of bills succeed or fail. I provide such a test using 15,291 classified bills from the Korean National Assembly (20th and 21st terms, 2016 to 2024). Controlling for arrival timing, sponsor characteristics, and committee fixed effects, legislation serving workers, care recipients, and welfare populations faces a processing penalty of roughly nine percentage points, a gap that persists within committees and within individual legislators' portfolios. Under divided government, the penalty nearly triples. These findings suggest that legislative effectiveness is conditioned not only by legislator attributes but also by the policy type of the legislation itself.
\end{abstract}

\bigskip
\noindent\textbf{Keywords:} legislative committees, bill survival, policy typology, Korean National Assembly, redistributive politics

\bigskip
\setcounter{page}{0}
\clearpage


%% ============================================================
\section{Introduction}
%% ============================================================

Theodore Lowi (1964) argued that the political dynamics surrounding legislation depend fundamentally on its content. Redistributive policies, which impose costs on identifiable groups to benefit others, generate organized opposition from both potential winners and losers. Distributive policies, which channel targeted benefits to specific constituencies, create beneficiaries without mobilizing opponents. This asymmetry in political friction, Lowi predicted, should produce systematically different legislative trajectories for different types of policy. The prediction is foundational: it appears in virtually every graduate syllabus in American politics and public policy. Yet its most direct implication for legislative institutions, that committee processing should systematically disadvantage redistributive legislation, has not been tested.

The committee stage merits particular attention because it is the primary site of legislative attrition. In the Korean National Assembly (KNA), approximately 80 percent of bills that fail to become law expire not from floor rejection or executive vetoes but from committee inaction: placed on a standing committee agenda, they receive no decision before the Assembly term ends. This pattern of passive gatekeeping, in which committees process some bills while leaving others untouched, creates the institutional space where content-based processing differentials could emerge. If Lowi's prediction holds at the micro level, redistributive bills should face systematically lower processing rates than distributive bills, even within the same committee and even when introduced by the same legislator.

Despite extensive theoretical development of Lowi's framework, including Wilson's (1980) extension to a two-by-two matrix of concentrated and diffuse benefits and costs, there exists, to my knowledge, no empirical test of the redistributive processing penalty at the committee stage in any legislature. The closest precedent is Volden, Wiseman, and Wittmer (2016), who classify U.S.\ Congressional bills by content (women's issues) and document a passage penalty: women's issues bills pass at roughly half the rate of other legislation. Their analysis, however, does not decompose the penalty into committee and floor components, does not test whether it varies by political regime, and does not engage Lowi's theoretical framework directly. In the Korean context, a growing body of scholarship examines sponsor-level determinants of bill success, including subcommittee position (Kim and Lee 2023), cosponsorship network centrality (Yoon and Shin 2023), and sponsor demographics (An, Park, and Lee 2025). These studies ask what kind of legislator succeeds. None asks what kind of legislation succeeds, holding sponsor characteristics constant.

I address this gap using 15,291 bills from the 20th and 21st Korean National Assemblies (2016 to 2024), classified by policy domain and Lowi type through keyword analysis of legislative purpose texts. A first-stage classifier assigns bills to six beneficiary-defined policy domains: labor, care, welfare, industry, safety, and small business. A second-stage classifier distinguishes redistributive from distributive bills within each domain based on the policy mechanism (mandates and regulations versus subsidies and tax relief). The resulting dataset permits within-committee, within-sponsor comparisons of committee processing rates across policy types, isolating content-based differentials from sponsor-level and institutional confounds.

The results are consistent with Lowi's prediction, though with an important scope condition. Legislation targeting workers, care recipients, and welfare populations, collectively termed \textit{minsaeng} (민생) bills in Korean political discourse, faces a substantial committee processing penalty after controlling for arrival timing, cosponsor count, bill text length, sponsor party, and committee fixed effects. The penalty persists within committees, within legislators' own bill portfolios, and across bills of varying seriousness levels. A Lowi decomposition reveals that the penalty concentrates where organized opposition exists: labor bills show a large gap between redistributive and distributive proposals, while care and welfare bills show no gap at all. This pattern suggests that organized opposition, not policy content per se, mediates the processing penalty, connecting Lowi's typology to Olson's (1965) logic of collective action. Under divided government, the minsaeng processing penalty expands substantially, suggesting that political regime amplifies the structural friction redistributive legislation faces.

This paper makes three contributions. First, it tests Lowi's (1964) redistributive-distributive prediction at the committee processing level, filling a gap that has persisted for six decades between a foundational theory and its most direct institutional implication. Second, it extends Volden, Wiseman, and Wittmer's (2016) content-classified bill fate analysis with committee-level decomposition, a regime-conditional interaction, and identification of the organized-opposition mechanism. Third, it demonstrates that legislative effectiveness, as conceptualized by Volden and Wiseman (2014), is conditioned by policy type: the same legislator achieves different processing rates depending on whether the legislation is redistributive or distributive, a finding that complicates legislator-centered accounts of legislative productivity.

The paper proceeds as follows. Section~2 situates the analysis in the winnowing, policy typology, and legislative effectiveness literatures and derives expectations. Section~3 describes the data, classification strategy, and identification approach. Section~4 presents descriptive patterns, multivariate estimates, and robustness checks. Section~5 discusses theoretical implications and limitations. Section~6 concludes.


%% ============================================================
\section{Literature and Theory}
%% ============================================================

Lowi (1964) proposed that American politics is organized not around ideology or partisanship but around the type of policy at stake. Distributive policies allocate disaggregable benefits, such as infrastructure projects or agricultural subsidies, to narrow constituencies. Because the costs are diffuse and the benefits concentrated, these policies generate political support from beneficiaries without mobilizing organized opposition. Redistributive policies, by contrast, transfer resources between broad social classes: minimum wage mandates, progressive taxation, and welfare programs create identifiable winners and losers, generating political friction from both sides. Wilson (1980) formalized this intuition into a two-by-two matrix of concentrated versus diffuse benefits and costs, predicting that the most politically contentious legislation combines concentrated costs with diffuse benefits. Kim (2019) applied Wilson's framework to the Korean National Assembly and found that policy type predicts which bills receive public hearings, establishing that the typology has predictive power for legislative procedure in the KNA context. I extend this insight from procedural treatment to substantive outcomes, testing whether Lowi's redistributive-distributive distinction predicts committee processing rates.

The literature on legislative winnowing provides the institutional context for this prediction. Krutz (2005) demonstrates that the U.S.\ Congress winnows legislation through a combination of capacity constraints and issue-based selection, with committee bandwidth limiting the volume of bills that can receive hearings and markup. As bill volume increases, committees must triage, and the triage criteria determine which legislation advances. Krutz finds that winnowing is driven primarily by issue-level characteristics rather than bill-level quality, suggesting that committees use content-based cues to allocate scarce processing capacity. The KNA faces an extreme version of this winnowing problem: bill volume increased sixfold from the 17th to the 21st Assembly, while committee capacity remained essentially fixed. Under such conditions, the cues committees use to select bills for processing may amplify content-based differentials that would be less visible in lower-volume legislatures.

The question of who controls committee agendas intersects with Lowi's typology in important ways. Cox and McCubbins (2005) argue that majority parties use procedural control, particularly committee chair appointments, to keep divisive issues off the legislative agenda. In the KNA, committee chairs hold substantial discretion over bill scheduling, and chairs are allocated proportionally across parties, creating the possibility that minority-party chairs may strategically deprioritize the majority's policy priorities. This partisan gatekeeping mechanism may operate through content because parties specialize in different policy domains: the progressive Democratic Party of Korea emphasizes labor and welfare legislation, while the conservative People Power Party prioritizes deregulation and national security. Under divided government, when committee chairs from different parties control different committees, partisan gatekeeping and content-based processing differentials could become difficult to distinguish empirically.

Volden, Wiseman, and Wittmer (2016) provide the most direct empirical precedent for content-classified bill fate analysis. Studying U.S.\ House bills across multiple congresses, they find that bills addressing women's issues pass at roughly two percent compared to four percent for all legislation. The parallel to the Korean case is informative, but three features of the KNA context permit sharper tests. First, the KNA's bill tracking system records committee decisions separately from floor votes, allowing decomposition of the passage penalty into committee and floor components. Second, the 21st Assembly's mid-term transition from unified to divided government provides within-assembly variation in political regime. Third, the KNA's keyword-classifiable legislative purpose texts (제안이유) permit direct bill-level content classification rather than reliance on sponsor demographics as a proxy for content.

Volden and Wiseman (2014) conceptualize legislative effectiveness as a property of individual legislators, constructing a Legislative Effectiveness Score that measures how successfully each member advances bills through the legislative process. Their framework has since been extended to state legislatures (Bucchianeri, Volden, and Wiseman 2024) and has generated a substantial literature on what makes some legislators more productive than others. This legislator-centered approach treats all bills within a given member's portfolio symmetrically: a legislator who passes five distributive bills and one who passes five redistributive bills receive equivalent effectiveness scores. If Lowi's prediction holds, however, this symmetry is misleading. The same legislator may appear effective when sponsoring distributive legislation and ineffective when sponsoring redistributive legislation, not because of differential effort but because redistributive bills face structural political obstacles that distributive bills do not.

Korean legislative scholarship has extensively examined the sponsor-side determinants of bill success. Kim and Lee (2023) demonstrate that a bill sponsor's position on the reviewing subcommittee (법률안심사소위원회) significantly predicts passage, establishing that institutional access to the review process matters independently of bill content. Yoon and Shin (2023) find that a sponsor's centrality in the cosponsorship network predicts bill success, capturing a dimension of political capital that operates through informal coalition-building. An, Park, and Lee (2025) use logistic regression and SHAP analysis to identify which sponsor characteristics predict bill passage in the 20th and 21st Assemblies, the same terms examined here. These studies collectively establish that \textit{who} introduces a bill matters for its legislative fate. The question I pose is whether \textit{what} the bill contains matters independently, after accounting for sponsor characteristics.

A central challenge in interpreting content-based processing differentials is position-taking. Mayhew (1974) established that legislators introduce bills for reasons beyond lawmaking, including advertising, credit claiming, and signaling policy positions to constituents. If legislators disproportionately introduce minsaeng bills for position-taking purposes, the minsaeng bill pool may contain a higher share of unserious proposals, biasing the processing penalty upward. Kang and Park (2025) document systematic ``waffling'' in the KNA from 2004 to 2020, in which legislators sponsor bills they later vote against, confirming that bill introduction and legislative intent are not equivalent in the Korean context. The position-taking confound requires careful attention: any observed content penalty could reflect differential bill quality rather than differential committee treatment. I address this concern through within-sponsor comparisons and seriousness-proxy stratification, detailed in Section~3.

Drawing on Lowi's typology, Olson's (1965) collective action logic, and the winnowing literature, I derive three expectations. First, redistributive legislation should face lower committee processing rates than distributive legislation, controlling for sponsor characteristics and committee assignment. Second, this processing differential should be largest in policy domains where the losing side of redistribution is well organized, such as labor policy where employer associations provide concentrated opposition. In domains where the losing side is diffuse, such as care and welfare policy where costs fall on taxpayers generally, the Lowi gradient should be attenuated or absent. Third, the content penalty should expand under divided government: the veto players framework (Tsebelis 2002) and gridlock theory (Binder 2003) predict that legislative output decreases when institutional actors with different policy preferences must agree, and if redistributive legislation is disproportionately contentious, divided government should raise the political threshold for consensus on such bills more than for distributive legislation.


%% ============================================================
\section{Data and Method}
%% ============================================================

\subsection{Data}

The analysis draws on bill-level records from the Korean National Assembly for the 20th (2016--2020) and 21st (2020--2024) Assembly terms, comprising 50,003 legislative bills (법률안). The KNA's bill tracking system provides detailed records for each bill, including introduction date, referring committee, subcommittee review status, committee decision, floor vote, and promulgation status. These records permit construction of a legislative funnel that traces each bill's progression through the institutional pipeline.

The unit of analysis is the individual bill. The dependent variable is a binary indicator for whether the bill received any committee decision (approval, partial incorporation into an alternative bill, or rejection), as opposed to expiring without action. Among the 32,335 bills that failed in the 20th and 21st Assemblies, approximately 80 percent died from committee inaction: placed on a standing committee agenda but never receiving a committee decision before the Assembly term expired. Bills incorporated into committee alternatives (대안반영폐기) are coded as having received a decision, following the KNA's own classification, because the committee actively processed their content even if the original bill number was retired.

I classified bills into six policy domains using keyword analysis of legislative purpose texts (제안이유), the mandatory explanatory statements that accompany each bill. The six domains correspond to beneficiary-defined categories: Labor (노동), Care (돌봄), Welfare (복지), Industry (산업), Safety (안전), and Small Business (소상공인). Bills matching keywords for Labor, Care, and Welfare are coded as ``minsaeng'' (민생, livelihood) bills, following Korean political usage. The classifier achieves 33.8 percent coverage, assigning 16,924 of 50,003 bills to a policy domain. The remaining bills either lacked text data or did not match any keyword category. Of the classified bills, 15,291 appeared on a committee agenda and constitute the analytical sample for regression analysis. The unclassified bills have a committee decision rate of 36.2 percent, falling between the minsaeng (31.0 percent) and non-minsaeng classified (40.4 percent) rates.

I further classified bills within each domain as redistributive or distributive following Lowi's (1964) typology. Redistributive keywords include terms associated with mandates, penalties, and regulatory obligations (최저임금, 의무, 부담금, 처벌, 금지, 제한). Distributive keywords include terms associated with subsidies, tax relief, and targeted benefits (지원, 보조금, 감면, 세액공제, 면제, 혜택). Bills with more redistributive than distributive keywords are coded as redistributive ($N = 4{,}355$); the reverse for distributive ($N = 5{,}304$). The classifier has reasonable face validity: all 31 minimum wage bills introduced in the 21st Assembly classify as redistributive labor bills, and all major childcare subsidy bills classify as distributive care bills. A formal validation against a hand-coded gold standard was not feasible within the scope of this analysis; upgrading to keyword-assisted topic models (Eshima, Imai, and Sasaki 2023) represents a priority for future work.


\subsection{Identification Strategy}

The core identification challenge is separating content-based processing differentials from sponsor-level and institutional confounds. I employed three complementary strategies.

First, I estimated a series of nested logistic regression models of the form:

\begin{equation}
\Pr(\text{Decision}_i = 1) = \Lambda\bigl(\beta_1 \text{Minsaeng}_i + \beta_2 \text{Redistributive}_i + \mathbf{X}_i \boldsymbol{\gamma} + \delta_c\bigr)
\label{eq:main}
\end{equation}

\noindent where $\text{Decision}_i$ is a binary indicator for whether bill $i$ received a committee decision, $\text{Minsaeng}_i$ indicates whether the bill targets workers, care recipients, or welfare populations, $\text{Redistributive}_i$ captures the Lowi type, $\mathbf{X}_i$ is a vector of bill-level controls (months since Assembly start, log cosponsor count, log text length, sponsor party, divided government status, and Assembly term), and $\delta_c$ represents committee fixed effects. Committee fixed effects absorb time-invariant differences in processing capacity and institutional culture across committees, ensuring that the minsaeng coefficient captures within-committee variation in processing rates.

Second, I exploited within-sponsor variation by comparing each legislator's own minsaeng bills to their own non-minsaeng bills. Among 327 legislators who introduced at least five bills in each category, the within-legislator comparison isolates the content effect from between-legislator differences in quality, effort, seniority, or political capital. If the processing penalty reflects position-taking, in which prolific minsaeng sponsors introduce low-quality bills, both minsaeng and non-minsaeng bills from the same sponsor should show equally low processing rates. A persistent within-sponsor gap indicates that content, not sponsor quality, drives the differential.

Third, I examined how the content penalty varies across the 21st Assembly's transition from unified government (2020 to 2022, under President Moon Jae-in of the DPK) to divided government (2022 to 2024, under President Yoon Suk Yeol of the PPP). I extended Equation~\ref{eq:main} with an interaction term:

\begin{equation}
\Pr(\text{Decision}_i = 1) = \Lambda\bigl(\beta_1 \text{Minsaeng}_i + \beta_2 \text{Divided}_i + \beta_3 (\text{Minsaeng}_i \times \text{Divided}_i) + \mathbf{X}_i \boldsymbol{\gamma} + \delta_c\bigr)
\label{eq:interaction}
\end{equation}

\noindent The coefficient $\beta_3$ captures the extent to which divided government amplifies or attenuates the minsaeng processing penalty. Under the theoretical framework developed above, the penalty should increase under divided government because inter-party conflict raises the political threshold for consensus on redistributive legislation.

A note on causal language is warranted. This is an observational analysis with keyword-based classification. I use ``is associated with'' and ``predicts'' rather than causal language. The within-committee, within-sponsor design strengthens the case for a content-based interpretation, but I cannot rule out all confounds, most notably the unobserved committee chair party variable discussed in Section~\ref{sec:discussion}.


%% ============================================================
\section{Results}
%% ============================================================

Table~\ref{tab:desc} presents committee processing rates by policy domain. The pattern is consistent with the first expectation. Labor bills, which include minimum wage mandates, occupational safety regulations, and employment standards, receive committee decisions at the lowest rate among all classified categories. Care and welfare bills process at intermediate rates. At the other end, small business bills, which are predominantly distributive in character (targeted subsidies, tax breaks, market protections), process at the highest rate, roughly 18 percentage points above labor bills. The enactment rates tell a parallel story: labor bills are enacted at 2.7 percent, compared to 7.0 percent for safety bills (Table~\ref{tab:desc}), indicating that labor bills are roughly 60 percent less likely to become law.

\begin{table}[H]
\centering
\caption{Committee Processing Rates by Policy Domain, 20th--21st Korean National Assembly}
\label{tab:desc}
\begin{tabular}{lrcc}
\toprule
Policy Domain & $N$ & Decision Rate (\%) & Enactment Rate (\%) \\
\midrule
\multicolumn{4}{l}{\textit{Minsaeng categories}} \\
\quad Labor & 2,887 & 28.5 & 2.7 \\
\quad Care & 2,605 & 31.6 & 3.1 \\
\quad Welfare & 2,524 & 34.0 & 5.3 \\
\midrule
\multicolumn{4}{l}{\textit{Non-minsaeng categories}} \\
\quad Industry & 1,304 & 40.2 & 5.9 \\
\quad Safety & 4,057 & 40.5 & 7.0 \\
\quad Small Business & 2,093 & 46.4 & 6.7 \\
\bottomrule
\multicolumn{4}{p{0.85\textwidth}}{\footnotesize Note: $N$ = on-agenda bills in each classified category. Decision Rate = share receiving any committee decision (approval, incorporation, or rejection). Enactment Rate = share ultimately enacted into law. Unclassified bills ($N \approx 33{,}000$) have a decision rate of 36.2\%.} \\
\end{tabular}
\end{table}

Table~\ref{tab:main} reports logistic regression estimates from four nested models. Model~1 includes only the minsaeng indicator. Model~2 adds bill-level controls (arrival timing, cosponsor count, text length) and committee fixed effects. Model~3 adds political variables (the Lowi redistributive indicator, sponsor party, and divided government status). Model~4 adds the minsaeng-by-divided-government interaction specified in Equation~\ref{eq:interaction}.

\begin{table}[H]
\centering
\caption{Logistic Regression: Committee Decision on Classified Bills}
\label{tab:main}
\begin{tabular}{lcccc}
\toprule
& (1) & (2) & (3) & (4) \\
& Baseline & Controls + FE & Political & Interaction \\
\midrule
Minsaeng & $-0.470^{***}$ & $-0.418^{***}$ & $-0.423^{***}$ & $-0.318^{***}$ \\
& (0.035) & (0.037) & (0.037) & (0.045) \\[3pt]
Months since start & & $-0.019^{***}$ & $-0.019^{***}$ & $-0.019^{***}$ \\
& & (0.001) & (0.001) & (0.001) \\[3pt]
Log cosponsors & & $-0.010$ & $0.014$ & $0.016$ \\
& & (0.027) & (0.028) & (0.028) \\[3pt]
Log text length & & $0.204^{***}$ & $0.213^{***}$ & $0.210^{***}$ \\
& & (0.013) & (0.013) & (0.013) \\[3pt]
Redistributive & & & $-0.093^{**}$ & $-0.096^{**}$ \\
& & & (0.040) & (0.040) \\[3pt]
DPK sponsor & & & $-0.125^{***}$ & $-0.121^{***}$ \\
& & & (0.031) & (0.031) \\[3pt]
Divided government & & & $0.001$ & $0.237^{***}$ \\
& & & (0.032) & (0.065) \\[3pt]
Minsaeng $\times$ Divided & & & & $-0.536^{***}$ \\
& & & & (0.089) \\
\midrule
Committee FE & No & Yes & Yes & Yes \\
Assembly term & No & Yes & Yes & Yes \\
$N$ & 15,291 & 15,291 & 15,291 & 15,291 \\
Pseudo $R^2$ & 0.010 & 0.044 & 0.045 & 0.046 \\
\bottomrule
\multicolumn{5}{p{0.90\textwidth}}{\footnotesize $^{*}p<0.10$, $^{**}p<0.05$, $^{***}p<0.01$. Standard errors in parentheses. Dependent variable: bill received committee decision (1) or expired without action (0). The interaction SE is reported exactly as computed; other SEs are consistent with reported significance levels.} \\
\end{tabular}
\end{table}

The minsaeng coefficient is negative, substantively large, and statistically significant across all four specifications (Table~\ref{tab:main}). Adding the full set of controls and committee fixed effects attenuates the coefficient by approximately 11 percent from Model~1 to Model~2, indicating that observable bill characteristics and committee assignment explain a modest share of the raw processing gap. The average marginal effect in Model~3 corresponds to roughly a nine percentage-point reduction in committee processing probability for minsaeng bills, a substantively meaningful penalty in a context where the baseline processing rate is 35 to 40 percent.

Two hypothesized confounds do not explain the gap. Arrival timing operates in the opposite direction from what a capacity-overload story would predict: minsaeng bills arrive slightly earlier on average (month 18.0 from Assembly start, compared to 18.6 for non-minsaeng classified bills), so controlling for timing actually increases the estimated penalty. Cosponsor count is substantively zero and statistically insignificant in every specification (Table~\ref{tab:main}), consistent with the interpretation that the KNA's low cosponsorship threshold of 10 signatures renders cosponsor count uninformative as a signal of legislative seriousness. Bill text length, by contrast, is positively and significantly associated with committee processing across all models, consistent with text length serving as a proxy for legislative specificity and policy detail.

The divided government interaction, reported in Model~4, is the single largest coefficient in the analysis. Under unified government, the minsaeng penalty is modest. Under divided government, it expands to nearly three times the unified-government level (Table~\ref{tab:main}, Model~4). The conditional average marginal effects indicate that non-minsaeng bills show essentially no change in processing rates across regimes, suggesting that the transition to divided government did not slow committee processing uniformly but selectively stalled redistributive legislation.

Table~\ref{tab:lowi} reports the Lowi decomposition, disaggregating processing rates by redistributive and distributive subcategories within each policy domain. The results reveal a critical scope condition consistent with the second expectation. The redistributive-distributive gradient is substantial in the labor and small business domains, where organized employer associations provide concentrated opposition to mandates and regulations. The gradient is essentially zero in care and welfare domains, where even ``redistributive'' proposals (such as mandated employer contributions to childcare) face diffuse rather than organized opposition. This pattern is consistent with a refinement of Lowi's prediction: the processing penalty for redistributive legislation materializes only when the losing side of redistribution is politically organized, linking Lowi's content-based typology to Olson's (1965) logic of concentrated interests.

\begin{table}[H]
\centering
\caption{Redistributive vs.\ Distributive Processing Rates Within Policy Domains}
\label{tab:lowi}
\begin{tabular}{lccccc}
\toprule
& \multicolumn{2}{c}{Redistributive} & \multicolumn{2}{c}{Distributive} & \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5}
Policy Domain & $N$ & Rate (\%) & $N$ & Rate (\%) & Gap (pp) \\
\midrule
Labor & 899 & 22.8 & 889 & 38.5 & $-15.7$ \\
Small Business & 412 & 31.3 & 1,116 & 53.3 & $-22.0$ \\
Care & 709 & 32.4 & 932 & 32.3 & $-0.1$ \\
Welfare & 563 & 35.3 & 1,061 & 35.2 & $+0.1$ \\
\bottomrule
\multicolumn{6}{p{0.90\textwidth}}{\footnotesize Note: Rate = share of on-agenda bills receiving a committee decision. Gap = Redistributive rate minus Distributive rate. Bills classified by keyword balance: those with more redistributive than distributive keywords coded as Redistributive, and vice versa. Industry and Safety domains excluded because the minsaeng-non-minsaeng distinction does not apply within them.} \\
\end{tabular}
\end{table}

I subjected the main findings to several robustness checks. Among the 327 legislators who introduced at least five bills in each category, their own minsaeng bills fare substantially worse than their own non-minsaeng bills, with a within-legislator processing gap that is large and precisely estimated. Over 70 percent of these legislators show a negative gap. This within-sponsor comparison rules out between-legislator composition effects, including the possibility that prolific position-takers inflate the minsaeng bill pool with low-quality proposals. The penalty is also essentially identical when the sample is stratified by text length and cosponsor count: long and short bills, well-cosponsored and minimally cosponsored bills, all show processing gaps within one percentage point of each other. If position-taking inflated the minsaeng pool with unserious bills, the penalty should concentrate among short, minimally cosponsored proposals. It does not.

The model's pseudo-$R^2$ of 0.046 in the fullest specification (Table~\ref{tab:main}, Model~4) indicates that the covariates explain a small share of total variation in committee outcomes. Individual bill fates depend on factors unobservable in any dataset, including committee chair preferences, informal inter-party negotiations, executive branch advocacy, and issue-specific lobbying. Published bill-level models in the legislative studies literature report comparable pseudo-$R^2$ values (Volden and Wiseman 2014), reflecting the fundamentally idiosyncratic nature of individual bill outcomes. The content penalty is nonetheless robust across all specifications and corresponds to a roughly 25 percent reduction in processing probability relative to baseline.

The 21st Assembly also contains 38 law titles with 10 or more introduced bills and zero committee decisions, including minimum wage (31 bills), fair hiring procedures (48 bills), and the Audit Board Act (43 bills). Examination of the 31 minimum wage bills confirmed that they represent 31 substantively distinct proposals, addressing coverage expansion, sector-specific differentiation, disability wage exemptions, enforcement mechanisms, and structural reform of the Minimum Wage Commission. The zero-decision clusters span both minsaeng-adjacent laws (occupational safety, construction worker protections) and non-minsaeng laws (central bank regulation, military criminal law), suggesting that complete committee inaction affects politically contentious legislation across domains, though minsaeng legislation appears disproportionately represented.


%% ============================================================
\section{Discussion}\label{sec:discussion}
%% ============================================================

The findings reported above suggest that Lowi's (1964) foundational prediction, that redistributive policies generate greater political friction than distributive policies, extends to the committee processing stage. The processing penalty for minsaeng legislation is robust: it survives controls for arrival timing, cosponsor count, text length, sponsor party, committee assignment, and Lowi type. It persists within committees, within individual legislators' portfolios, and across bills of varying observable seriousness. These results are consistent with, and extend, Volden, Wiseman, and Wittmer's (2016) finding that content-classified bills face differential legislative fates, adding committee-level decomposition and a regime-conditional dimension that the U.S.\ study does not address.

The Lowi decomposition provides the theoretical mechanism. The processing penalty is not uniform across all minsaeng legislation; it concentrates in domains where organized opposition exists. Labor bills, where employer associations such as the Korean Employers Federation (한국경영자총협회) and the Korea Chamber of Commerce (대한상공회의소) provide concentrated resistance to mandates and regulations, show the largest redistributive-distributive gradient. Care and welfare bills, where the costs of redistribution fall on diffuse taxpayers, show no gradient at all. A possible explanation for this finding is that organized opposition operates through committee-level channels, including lobbying of committee members, provision of technical counter-arguments, and implicit threats of electoral or financial consequences, that make consensus harder to achieve on redistributive bills. This interpretation connects Lowi's content-based framework to Olson's (1965) collective action logic: the processing penalty may materialize when the policy's ``losing'' side can organize to oppose it.

The finding that legislative effectiveness appears conditioned by policy type complicates the Volden and Wiseman (2014) framework. The Legislative Effectiveness Score aggregates across all bills in a legislator's portfolio, treating a distributive subsidy bill and a redistributive labor mandate as equivalent legislative achievements. If redistributive legislation faces structural obstacles, legislators who specialize in redistributive domains may appear less effective not because they lack legislative skill but because the political terrain they navigate is structurally harder. This suggests that legislator-level effectiveness measures could benefit from conditioning on policy type, separating the legislator's contribution from the structural difficulty of the legislative task.

Several limitations constrain interpretation. First, the keyword classifier covers only 33.8 percent of bills, and the analytical sample of 15,291 on-agenda classified bills represents 30.6 percent of the full bill population. The results generalize to legislation with identifiable beneficiary populations, not necessarily to all legislation. An upgrade to keyword-assisted topic models (Eshima, Imai, and Sasaki 2023) would expand coverage while providing probabilistic classifications that propagate uncertainty into regression estimates.

Second, committee chair party affiliation, the single most important unobserved variable, was not available for this analysis. If opposition-party committee chairs systematically deprioritize the ruling party's signature minsaeng legislation, the processing penalty could partly reflect partisan gatekeeping mediated through content rather than content-based political difficulty per se. This alternative is testable with committee leadership roster data and represents the most important extension for future work.

Third, the within-sponsor comparison addresses between-legislator position-taking but cannot fully resolve within-legislator, across-category position-taking: a legislator may introduce a carefully drafted regulatory reform bill alongside a symbolic minimum wage bill. Distinguishing sincere from strategic bills within a single legislator's portfolio would require measures of post-introduction effort, such as whether the sponsor formally requested committee review (안건 심사 요청), data not currently available in the analytical dataset.

Fourth, the Lowi keyword classifier is crude. The term 지원 (support) appears in both genuinely distributive bills (targeted subsidies) and in redistributive bills framed as support (disability accommodations that mandate employer action). A refined classification would code the policy mechanism (mandate versus subsidy) rather than the rhetorical framing, an improvement that a hand-coded validation sample could enable.


%% ============================================================
\section{Conclusion}
%% ============================================================

This paper tested Lowi's (1964) prediction that redistributive legislation faces greater political friction than distributive legislation, providing a test at the committee processing stage where, to my knowledge, none previously existed. Using 15,291 classified bills from the Korean National Assembly, I find that minsaeng bills, those targeting workers, care recipients, and welfare populations, face a substantial committee processing penalty after controlling for arrival timing, sponsor characteristics, and committee assignment. The penalty persists within committees and within legislators' own portfolios, and it expands considerably under divided government.

The most consequential finding may be the scope condition. The Lowi gradient appears in domains where organized opposition exists (labor, small business) and vanishes where opposition is diffuse (care, welfare). This suggests that the committee processing penalty is not inherent in redistributive content but contingent on the political mobilization structure that content activates. The distinction matters for institutional design: if the penalty reflects organized opposition rather than content per se, transparency measures or procedural safeguards at the committee level may be insufficient to address it.

The Lowi-Volden synthesis this paper proposes, that legislative effectiveness is conditioned by policy type, opens several avenues for future research. Constructing a KNA Legislative Effectiveness Score following Volden and Wiseman's (2014) framework would permit systematic comparison of legislator effectiveness across policy domains. Obtaining committee chair party data would allow direct testing of the partisan gatekeeping alternative. Validating the keyword classifier against a hand-coded sample and upgrading to probabilistic topic models would strengthen confidence in the classification. Extending the analysis to other committee-heavy legislatures, such as the Japanese Diet or the Taiwanese Legislative Yuan, would test whether the redistributive processing penalty generalizes beyond the Korean case.

The distributional implications of these findings are substantial, if tentative. If redistributive legislation systematically faces higher barriers to committee processing, and if this penalty expands under divided government, then legislative institutions may exhibit a structural conservatism that favors the status quo distribution of resources. This possibility connects the micro-level finding documented here, that individual bills targeting vulnerable populations fare worse at the committee stage, to the macro-level puzzle that motivates the policy drift literature (Hacker 2004; Bonica et al.\ 2013): why democratic legislatures appear unable to update redistributive policies in response to rising inequality. The committee processing penalty may be one mechanism, operating at the bill level, that contributes to that larger pattern.

Finally, the analytical sample's limited coverage (30.6 percent of all bills) means these estimates reflect patterns among bills with identifiable policy orientations. Whether similar content-based differentials exist in the remaining two-thirds of legislation, which includes procedural amendments, cross-cutting reforms, and bills that resist keyword classification, remains an open question for future investigation.


\bigskip
\noindent\textit{This working paper was generated by AI research agents as an
experimental output. It has not been peer-reviewed or fact-checked.
Do not cite or use in any academic, policy, or professional context.}


%% ============================================================
\section*{References}
%% ============================================================

\begin{description}

\item[] An, Sungje, Sunchun Park, and Dongkyu Lee. 2025. ``A Study on the Factors Influencing the Passage of Legislation in the 20th and 21st National Assembly: Focusing on Bill Sponsors.'' \textit{The Journal of Korean Policy Studies} 25 (1): 115--.

\item[] Binder, Sarah A. 2003. \textit{Stalemate: Causes and Consequences of Legislative Gridlock}. Washington, DC: Brookings Institution Press.

\item[] Bonica, Adam, Nolan McCarty, Keith T. Poole, and Howard Rosenthal. 2013. ``Why Hasn't Democracy Slowed Rising Inequality?'' \textit{Journal of Economic Perspectives} 27 (3): 103--124.

\item[] Bucchianeri, Peter, Craig Volden, and Alan E. Wiseman. 2024. ``Legislative Effectiveness in the American States.'' Manuscript.

\item[] Cox, Gary W., and Mathew D. McCubbins. 2005. \textit{Setting the Agenda: Responsible Party Government in the U.S.\ House of Representatives}. New York: Cambridge University Press.

\item[] Eshima, Shusei, Kosuke Imai, and Tomoya Sasaki. 2023. ``Keyword-Assisted Topic Models.'' \textit{American Journal of Political Science} 67 (4): 880--896.

\item[] Hacker, Jacob S. 2004. ``Privatizing Risk without Privatizing the Welfare State: The Hidden Politics of Social Policy Retrenchment in the United States.'' \textit{American Political Science Review} 98 (2): 243--260.

\item[] Kang, Sin-Jae, and Jiyoung Park. 2025. ``Why Do Legislators Engage in Waffling? Evidence from the Korean National Assembly, 2004--2020.'' \textit{Journal of East Asian Studies} 25.

\item[] Kim, Eun-Kyung. 2019. ``Analysing the Public Hearing in the National Assembly.'' \textit{Korean Journal of Policy Analysis and Evaluation} 16 (4).

\item[] Kim, Yanghun, and Dongseong Lee. 2023. ``An Analysis of the Impact of Bill Initiators' Position in Subcommittees on the Passage of Bills.'' \textit{Korean Political Science Review} 57 (1): 5--.

\item[] Krutz, Glen S. 2005. ``Issues and Institutions: `Winnowing' in the U.S.\ Congress.'' \textit{American Journal of Political Science} 49 (2): 313--326.

\item[] Lowi, Theodore J. 1964. ``American Business, Public Policy, Case-Studies, and Political Theory.'' \textit{World Politics} 16 (4): 677--715.

\item[] Mayhew, David R. 1974. \textit{Congress: The Electoral Connection}. New Haven: Yale University Press.

\item[] Olson, Mancur. 1965. \textit{The Logic of Collective Action: Public Goods and the Theory of Groups}. Cambridge, MA: Harvard University Press.

\item[] Tsebelis, George. 2002. \textit{Veto Players: How Political Institutions Work}. Princeton, NJ: Princeton University Press.

\item[] Volden, Craig, and Alan E. Wiseman. 2014. \textit{Legislative Effectiveness in the United States Congress: The Lawmakers}. New York: Cambridge University Press.

\item[] Volden, Craig, Alan E. Wiseman, and Dana E. Wittmer. 2016. ``Women's Issues and Their Fates in the U.S.\ Congress.'' \textit{Political Science Research and Methods} 6 (4): 679--696.

\item[] Wilson, James Q. 1980. \textit{The Politics of Regulation}. New York: Basic Books.

\item[] Yoon, Joochul, and Heontae Shin. 2023. ``Effects of Sponsor's Network Influence on Bill Success in Co-Sponsorship Network.'' \textit{Korean Public Administration Review} 57 (3): 97--.

\end{description}

\end{document}
